\chapter{Conclusion}

\textit{In this chapter, we will present the conclusion of the project.}\newline
\\
The problem definition states:
\begin{quote}
How can we ease the daily life for children with ASD and their guardians, while complying with the study regulation?
\end{quote}

We have designed a product that should help ease the use of pictograms. 
PARROT should help organize and ease access and use of pictograms. This allows for many of these to be handled simultaneously, without the need of the many physical pictograms and their bulky folders as mentioned in the analysis.\newline
It also gives the functionality to play sound, which could help some of the children learn the spoken language while using the pictograms to communicate. 
The idea of handling pictograms digitally also opens opportunities otherwise not easily accessible for the guardians.
For instance, we can change PARROT's colors according to the needs of the individual child. This include the colors for the different categories as well as those of the speech board.
The guardian can modify the categories and organize them according to the needs of the child.\newline
Since we have developed an application based on the needs of a third party, have been part of a multi project, and have performed dynamic blackbox testing as well as whitebox usability testing, we have upheld the goals of the study regulation.\newline

The whole project have been part of a greater multi project with five groups participating. 
As such we have not made a individual product, but one that is part of a greater product, GIRAF.  
GIRAF is not yet finished, but is hopefully going to be continued by other students on future semesters, so that it can become a product worthy of being used in the aforementioned institutions.\newline
As part of the multi project we have been using an agile development method, SCRUM.
Using SCRUM we have not spent the start of the semester analyzing the whole system, and designing it from the start. Instead we have analyzed and designed parts of the system one sprint at the time.
In previous semesters, we have wasted time on analyzing functionality that was never written, which was not the case in this semester.\newline
\\
\textit{This chapter presented the conclusion.}