\section{Managing Categories} %%Name of Feature.
\label{mc}
\subsection*{Problem}
When more and more pictograms are added to PARROT, the categories can help manage and organize these pictograms. 
The categories help manage the different users's needs, so for every user, the categories can differ. 
We therefore need to be able to configure categories to suit the different users's needs, as well as createing new categories. 
There is also the need to remove unwanted categories from a user's profile.


\subsection*{Solution}
To do this, we use the combination of buttons, and drag and drop. 
Functionality like deleting categories and pictograms, and adding pictograms from one category to another is done via drag and drop. 
Creating new categories and changing information about the categories is done using buttons. 


\subsection*{Execution}
We will first describe the drag and drop functionalities. 
When we want to delete a specific pictogram from a category, we choose the pictogram from the gridview, and drag it to the trashcan. 
In the DROP part of the listener, we check if the drop zone are the trashcan, and that the dragged object is from the gridview.
When we know this, we create a temporary category, where we save the information of the category we are currently modifying. We then remove the pictogram, and overwrite the old category with this new information.
This can be seen in Source Code \ref{mc1}.

\begin{source}[{mc1}]{Deleting a pictogram from a category}
if(self.getId()==R.id.trash && ManageCategoryFragment.catDragOwnerID == R.id.pictograms) //We are to delete a pictogram from a category
				{
					Category temp = ManageCategoryFragment.profileBeingModified.getCategoryAt
						(ManageCategoryFragment.currentCategoryId);
					
					temp.removePictogram(ManageCategoryFragment.draggedItemIndex);
					
					ManageCategoryFragment.profileBeingModified.setCategoryAt
						(ManageCategoryFragment.currentCategoryId, temp);
					
					pictograms.setAdapter(new PictogramAdapter(ManageCategoryFragment.profileBeingModified.
						getCategoryAt(ManageCategoryFragment.currentCategoryId), parrent));
				}
\end{source}

When we want to copy a picogram from one category into another category, we choose the category we want to copy from, and drag the chosen pictogram onto the category that we want to copy the pictogram to. 
Still in the DROP part of the listener, we check if the drop zone is the categories, and if the dragged object is from the gridview showing the pictograms.
To know what category we are dropping the pictogram into, we need to know the index of the category, which we do by coordinates of the drop, and referencing to the index of the list.
We then add the pictogram to the category at the index.
This can be seen in Source Code \ref{mc2}.

%% get code from ManagementBoxDragListener.java lines 52 - 66

\begin{source}[{mc2}]{Copying a pictogram into another category}
else if(self.getId()==R.id.categories && ManageCategoryFragment.catDragOwnerID == R.id.pictograms) //We are to copy a pictogram into another category
				{
					
					draggedPictogram = ManageCategoryFragment.profileBeingModified.getCategoryAt
						(ManageCategoryFragment.currentCategoryId).getPictogramAtIndex
						(ManageCategoryFragment.draggedItemIndex); 
							
					ListView categories = (ListView) parrent.findViewById(R.id.categories);
					int x = (int)event.getX();
					int y = (int)event.getY();
					int index = categories.pointToPosition(x, y);
					
					Category temp = ManageCategoryFragment.profileBeingModified.getCategoryAt(index);
					
					temp.addPictogram(draggedPictogram);
				
					ManageCategoryFragment.profileBeingModified.setCategoryAt(index, temp);
										
				}
\end{source}
When we want to copy all pictograms from one category into another category, we first choose the category which we want to copy to. 
Then we drag the category into the gridview showing the pictograms. 
Also in the DROP part of the listener, we check if the drop zone is the gridview showing the pictograms, and that the dragged object is from the categories.
We then initialize two category objects. 
One containing the category from which we want to copy, which we call categoryCopiedFrom, and one containing the category we want to copy to ,which we call temp. 
We then go through the pictograms in categoryCopiedFrom, and add these pictograms to temp. 
When all pictograms are copied, we overwrite the old category we wanted to copy from with the new temp category. 
This can be seen in Source Code \ref{mc3}.

%% get code from ManagementBoxDragListener.java lines 67 - 81
\begin{source}[{mc3}]{Copying a category into another category}
else if(self.getId()==R.id.pictograms && ManageCategoryFragment.catDragOwnerID == R.id.categories) //We are to copy a category into another category
				{	
					
					Category categoryCopiedFrom = ManageCategoryFragment.profileBeingModified.getCategoryAt
						(ManageCategoryFragment.draggedItemIndex); 
					
					Category temp = ManageCategoryFragment.profileBeingModified.getCategoryAt
						(ManageCategoryFragment.currentCategoryId);
					
					for(int i = 0; i < categoryCopiedFrom.getPictograms().size(); i++)
					{
						temp.addPictogram(categoryCopiedFrom.getPictogramAtIndex(i)); 
					}
					
					ManageCategoryFragment.profileBeingModified.setCategoryAt
						(ManageCategoryFragment.currentCategoryId, temp);
					
					pictograms.setAdapter(new PictogramAdapter
						(ManageCategoryFragment.profileBeingModified.getCategoryAt
						(ManageCategoryFragment.currentCategoryId), parrent));
				}
\end{source}
When we want to delete a category, we drag the chosen category into the trashbin. 
In the DROP part of the listener, we check if the drop zone is the trashbin, and that the dragged object is from the category grid. 
We then remove the category from the profile that we are currently modifying. 
This can be seen in Source Code \ref{mc4}:

%% get code from ManagementBoxDragListener.java lines 82 - 86
\begin{source}[{mc4}]{Deleting a category}
else if(self.getId()==R.id.trash && ManageCategoryFragment.catDragOwnerID == R.id.categories) //We are to delete a category
				{	
					ManageCategoryFragment.profileBeingModified.removeCategory
						(ManageCategoryFragment.draggedItemIndex);
					
					categories.setAdapter(new ListViewAdapter(parrent, R.layout.categoriesitem,
						ManageCategoryFragment.profileBeingModified.getCategories()));
				}
\end{source}
When we want to change the icon of a category, we choose a pictogram from the gridview and drag into the space for the icon, which replaces the current icon. 
In the DROP part of the listener, we check if the drop zone is the Icon ImageView, and the dragged object is from the gridview showing the pictograms. 
If so, we notice what index the dragged object has, and create a temporary category. 
In this category we set its icon to be that of the dragged object.  
We then overwrites the old category with the temporary category.
Then we begin to draw the new icon in the ImageView so that it can be seen. 
This can be seen in Source Code \ref{mc5}.

%% get code from ManagementBoxDragListener.java lines 87 - 97
\begin{source}[{mc5}]{Changing the category icon.}
else if(self.getId()==R.id.categorypic && ManageCategoryFragment.catDragOwnerID == R.id.pictograms) //We are to change the icon of the category
				{
					draggedPictogram = ManageCategoryFragment.profileBeingModified.getCategoryAt
						(ManageCategoryFragment.currentCategoryId).getPictogramAtIndex
						(ManageCategoryFragment.draggedItemIndex);
					
					Category tempCat = ManageCategoryFragment.profileBeingModified.getCategoryAt
						(ManageCategoryFragment.currentCategoryId);
					
					tempCat.setIcon(draggedPictogram);
					
					ManageCategoryFragment.profileBeingModified.setCategoryAt
						(ManageCategoryFragment.currentCategoryId, tempCat);
					
					ImageView icon = (ImageView) parrent.findViewById(R.id.categorypic);
					
					icon.setImageBitmap
						(ManageCategoryFragment.profileBeingModified.getCategoryAt
						(ManageCategoryFragment.currentCategoryId).getIcon().getBitmap());
					
					ListView list = (ListView) parrent.findViewById(R.id.categories);
					
					list.setAdapter(new ListViewAdapter(parrent, R.layout.categoriesitem,
						ManageCategoryFragment.profileBeingModified.getCategories()));
				}
\end{source}
We will now describe the functions that are activated via buttons.
When we want to create a new category, we simply push the "create new category" button. 
We use a onClikListener in ManageCategoryFragment.
When the button is pushed it creates a new category for the profile currently being chosen, as well as some information needed to create such a category. 
We create a empty pictogram to be used as its icon, sets its name to "kategori navn", and its color to red. 
This can be seen in Source Code \ref{mc6}.

%% get code from ManageCategoryFragment.java lines 165 - 175
\begin{source}[{mc6}]{Creating a new category}
createNewCategory.setOnClickListener(new OnClickListener() 
		{
			public void onClick(View v) 
			{
				Pictogram pictogram = new Pictogram("#usynlig#", null, null, null, parrent);
				
				Category cat = new Category("Kategori Navn", 0xffff0000, pictogram);
				
				profileBeingModified.addCategory(cat);
				
				ListView categories = (ListView) parrent.findViewById(R.id.categories); //Redrawing the categories
				
				categories.setAdapter(new ListViewAdapter(parrent, R.layout.categoriesitem, profileBeingModified.getCategories())); 
				//Adapter for the category gridview
			}
		});
\end{source}
When we want to change the color of a category we push the "Change Category Color" button. 
For this we also use a onClikListener, which activates a pop up screen where it is possible to choose the color. This pop up screen is described in \autoref{colpic}.
We then save the output from this into the category as its background color. 

\subsection*{Result}
We are now able to manipulate, organize and manage categories. We can create and delete categories,
add and delete pictograms to them, add all pictograms from one category into another, and 
change the categories icon as well as background color.


\subsection*{Notes}
The functionality of changing a category's icon was first designed to be a button. We changed this while coding because it seemed more intuitive.\newline 
Unfortunately, there is some functionality that is not yet finished. And although the buttons are in the design they do not do anything. 
These functionalities include the spinner, which should have made it possible to change what profile was being modified, as well as the buttons making it possible to change the title of categories, copy a category from another profile, and copy the current category to another profile. 


\subsection*{Further Reading}
Drag and drop are used in these functions. It can be found at \autoref{dnd}.