\chapter{Application Design}
Based on the original design for the Digi-Pecs application, modified by the information gathered in the previous chapters, we have come up with the general idea for how we want the design for PARROT to be.\newline
First of all, we want the application to be safe, simple to use, and easy to remember.\newline
By \textit{safe}, we mean that the users of the system should only have access to their own area. For instance, a child user should not (commonly) have access to the options and administation parts of the application, while guardians should not have access to the profiles of other guardians, or children not under their supervision.\newline
For the system to be \textit{simple to use} and \textit{easy to remember}, we want the application to have a relatively simple user interface. Especially because the application is meant to be used by children with autism. Furthermore, the reason for making this application is to make the daily use of pictograms easier. This goes for the guardians as well. If they can't use the system, the children will not be able to learn how to use it.\newline
It is not our thought that the system has to be intuitive, but it is our opinion that if the user is provided by a short demonstation or manual, they will master the concepts of the application in no time.\newline
\\
Designing the user interface has been an iterative process, such is the method of SCRUM. We started by having a look at the design from the report of the previous year (we were unable to see the actual design) and compared it to the tools shown to us by Tove Søby.%skal der refereres ved navn?
We decided that we wanted our design to look and feel like the real thing, so we drew up a quick sketch of how the system would look in our opinion.\newline
%indsæt billede
As seen in the picture, we wanted a speechboard to show the current available pictograms, a sentenceboard to put the pictograms on to create a sentences, and a number of tabs representing different categories of pictograms. We also put a play-button on the design, so that the user could press it to play out the sentence.\newline
The reason for this choice was based on the idea of having the system be as close to the existing tools as possible. The guardians already have speechboards and sentenceboards, and they have lots of folders containing pictograms organized into different categories. This is why we went for the tab style of the categories, as that would make it look more like a folder.\newline
As we began implementing the system, we realised that we had to make several changes. First of all, the size of the initial sentenceboard was too small, it would have to be bigger in order to make the pictograms easily visible. Also, we had to change the design from tabs to buttons, as we discovered that Android does not natively support vertical tabs. We also removed the play-button, mainly because our contact said that she would rather have the ability to play each pictogram one at a time, than only the ability to play the entire sentence. Also, the button took up a lot of the already limited space on the interface.\newline
\\
After the initial design phase, and early implementation 