\section{Future Work}
\begin{itemize}
	\item Show and Edit Category names.
	\item Add Profile icon to design.
	\item Check with customers/experts if the drag drop functionality with sentences are handled correctly.
		\subitem Or make it possible to change how the sentenceboard functionality should work for the individual child.
	\item Remove the DragShadow when dragging an empty Pictogram
	\item Create a startup screen while loading
	\item Create a busy animation
		\item This one could be common for all apps for the GIRAF platform.
	\item Handle color from launcher and make those standard colors in PARROT.
		\subitem this could be a replacement for AmbilWarna, or in addition to it.
	\item Consider changing the Category class, so that categories can contain categories.
	\item Write search functionality for pictograms, and use tags.
	\item Expand the Options fragment.
		\subitem Remember to save all changes to the PARROTProfile.
	\item Finish connecting the application to the launcher.
	\item Add camera functionality.
	\item Make the Spinner on the management fragment work, so that it contains all the children profiles for the active guardian.
	\item write the functionality for the unimplemented buttons on the management fragment.
	\item Expand the options fragment, so that the children can be more individualized.
		\subitem For instance, add functionality to limit the access to the individual tabs.
	\item Note that the name of the root folder might not be sdcard/ on add Android units.
		\subitem consider using Enviroment.get(...) to make the paths hardware independant.
	\item Add mute functionality.
	\item Add guardian mode in child mode.
	\item Homogenize the design, so that all the fragments have the same design format.
		\subitem For instance, the speechboard has round corners, while the others have hard corners.
	\item Suggest to the Admin group that Pictograms and Categories are made part of the database.
	\item Fix the bug that causes the system to crash when the user has no categories.
	\item Fix the bug that causes the system to crash when a category is copied into itself.
\end{itemize}


