\section{Target Platform}
In this learning project we are developing applications, for children with autism, using the android platform. The android platform was chosen because this project is part of a multi project which began the development of the Giraf system \cite{SW6Android2012}.

Android is an open-source platform developed for mobile devices. The Android Open Source Project(AOSP) is maintained and further developed by the Open Handset Alliance(OHA), which is led by Google \cite{androidPhilosophy}. The companies from the OHA contributes to the project, these contributions are often made in form of engineering resources.

Android has a large community, spread over various websites, with different areas of expertise. This provides developers of android applications a community where they can find help with their niché \cite{androidCommunity}.
Google, which is head of the android development, also has a website for teaching app developers how to program for android \cite{androidDevelopers}. On Google’s website they also provide various tutorials, so one can easily get started developing for android.

In this project we have been provided with several Samsung Galaxy Tab 10.1 
\cite{tablet}. The firmware on the tablets are version 3.2 \cite{android32}. This version has been chosen because it is the first version developed mainly for tablets, and it is going to be supported for the duration of the project.
Version 3.2 provides some new features, which are:
\begin{itemize}
	\item Statusbar notifications.
	\item Hardware acceleration.
\end{itemize}
