\section{Target Group}
Autism is a spectrum disorder meaning that, the degree of disorder can be different \cite{autism.about.com1}. Autism can affect people in different ways, i.e. it can make them more chatty or silent, more methodical or disorganized. Lisa Jo Rudy, researcher, consultant, and mother to a child with autism, states \cite{autism.about.com2} that: ''if you've met one person with autism, you've met one person with autism''.

The Autism Society of America defines autism \cite{definitionOfAutism} as follows: ''Autism is a complex developmental disability that typically appears during the first three years of life and is the result of a neurological disorder that affects the normal functioning of the brain, impacting development in the areas of social interaction and communication skills. Both children and adults with autism typically show difficulties in verbal and non-verbal communication, social interactions, and leisure or play activities.

Autism is one of five disorders that falls under the umbrella of Pervasive Developmental Disorders (PDD), a category of neurological disorders characterized by severe and pervasive impairment in several areas of development.''

Children with autism are usually very fixated in a single area, meaning that they can become very interested in one area and thereby completely forget or ignore the world around them, which can lead to unintended behavior. This fixation can be used by educators or teachers to motivate the children to learn, by including this area of interest into the learning process.

   Children with autism may also have difficulties socializing with people, feeling empathy, and understanding other peoples feelings. Lastly children with autism often wants to structure everything because they have a need for a structured environment, which is also an important aspect during the planning of their everyday.
   
\subsection{Working with Children with Autism}
This section is based upon the statements of a woman with autism \cite{autism.com}, explaining what it is like to live with autism, and an interview with an educator at Birken, a special kindergarten for children with autism (see appendix \ref{InterviewMette} for interview notes).

	People with autism are often more visual in their way of thinking. Rather than visualizing thoughts in language and text, they do it in pictures or visual demonstrations. Pictures and symbols are therefore an essential part of the daily tools used by children with autism and the people interacting with them. Also, children with autism can have difficulties expressing themselves by writing or talking, and can often more easily use electronic devices to either type a sentence or show pictures, to communicate with people around them.

Different communication tools for children with autism already exist, but many of them rely on a static database of pictures, and often these has to be printed on paper in order to use them as intended. Other tools, such as hour glasses of different sizes and colors, are also essential when working with children with autism, and these tools are either brought around with the child, or a set is kept every place the child might go, being at an institution or at home.
Because this need of many different tools exist, it is relevant to explore the possibilities in using android tablets with customizable software as a tool for children with autism and the people working with them.