\section{Motivation}
This is a student report written as part of a learning project.
We are required to comply with the study regulation, which states that the main focus of this semester is multi-project management and quality assurance in the form of requirements analysis, requirements management, and testing.\\
The goal is to create a comprehensive software system, across multiple project groups, in order to enhance our competences in analysis, design, implementation, and evaluation of software applications in regards to the system requirements. \cite{studyreg}

To create a comprehensive system that will be usable in real life scenarios, this project will build on top of a previous multi-group project and will also be built with the aim of having other students continue its development later.
Picking up and passing on application development within the system will make it possible to make them far more complex and by extend provide them with all of the necessary functions for them to be viable alternatives to tools that may exist already, as opposed to creating only ``single semester sized'' apps within the same system.\\
  
The multi-group project we are building on top of is aimed at creating a touch based tablet system to support children with autism and their guardians in every day scenarios.
In order to describe the context of this system we will in rest the introduction we will explore: 
\begin{description}
	\item[Target Group:] The group of people we hope to assist with our system.
	\item[Target Platform:] What platform will be the best for our system.
	\item[Development Method:] Which method that will serve us best in developing the system.
	\item[System Description:] The description of the areas we will be developing.
	\item[External Component Structure:]
\end{description}