\chapter{The Process}
\label{ch:SprintProcess}
In this chapter we describe the sprint process of our project, this can be seen in Section \vref{sec:sprints}.

\section{Sprints}
\label{sec:sprints}
This project was divided into eight sprints. The length of the sprints was decided at every sprint meeting. At the end of each sprint period, a meeting was held to reflect on what was learned through the sprint. The Burndown Charts, Sprint Backlogs and the final change log can be seen in Appendix \vref{sec:burn_back}.

\subsection{Sprint One}
Sprint one started on 19/03-2012 with a workperiod of seven half days. In this sprint period we started making the design for the Oasis Local Db schema, a prototype database, the model classes, that is supposed to wrap the data from the Oasis Local Db, and some methods to the library, which we got as requirements from the other groups.

\subsubsection{Sprint Reflection}
In this sprint we learned that we should be a bit better at estimating the size of each task and the solution would be combining the small tasks into bigger tasks, thereby allowing us to work on one big task a day, instead of several small tasks.

\subsection{Sprint Two}
Sprint two started on 26/03-2012 with a workperiod of eight half days. In this sprint period we improved the design for the Oasis Local Db schema, started implemting the Oasis Local Db, and updated the library with the new requirements we got from the other groups. 
Besides that we used a little time on setting up a counter-strike server, this gave us a social activity that improved the relation between the multi project groups.

\subsubsection{Sprint Reflection}
In this sprint we learned that we still should be a bit better at estimating the size of each task, because there was some tasks we did not start on.
Another thing we learned was that a good database design takes some iteration to achive.

\subsection{Sprint Three}
Sprint three started on 10/04-2012 with a workperiod of nine half days. In this sprint period we froze the Oasis Local Db schema, continued on the implementation of the Oasis Local Db, and updated the Oasis Lib with the new requirements gathered from the other groups. 
Besides that we started thinking on the ``Oasis App''.

\subsubsection{Sprint Reflection}
In this sprint we learned that we should not be adding new tasks to the sprint backlog when the sprint has started, as this will make us less likely to complete all tasks on the sprint backlog.
Besides that, we overestimated the size of the tasks, which lead to tasks not being completed before the end of the sprint.
Another thing we learned was that some tasks depended on each other and this could result in some tasks not being completed because of such a dependency.

\subsection{Sprint Four}
Sprint four started on 23/04-2012 with a workperiod of six half days. In this sprint period we completed the implementation of the Oasis Local Db and updated the Oasis Lib with the new requirements gathered from the other groups. Besides that we started writing JavaDoc to the Oasis Lib, refactored the code in the Oasis Local Db, started making a method, which created dummy data, and wrote a part of the common report.

\subsubsection{Sprint Reflection}
In this sprint we learned that we still need to be better at saying no to other groups, whom came with new tasks in the middle of the sprint.

\subsection{Sprint Five}
Sprint five started on 07/05-2012 with a workperiod of six half days.
In this sprint we worked on implementing the Oasis App.
We also planned to work on synchronizing with Savannah, however this did not happen due to Savannah not being ready.
The Oasis Lib was improved with minor bug fixes.

\subsubsection{Sprint Reflection}
In this sprint we learned to communicate with the other groups before planning a mutual task.

\subsection{Sprint Six}
Sprint six started on 14/05-2012 with a workperiod of eight half days. In this sprint we continued the implementation of the Oasis App, updated the Oasis Lib, and started creating a structure for the rapport.

\subsubsection{Sprint Reflection}
In this sprint we learned nothing new.

\subsection{Sprint Seven}
Sprint seven started on 21/05-2012 with a workperiod of nine half days.
In this sprint we worked on unit tests for the Oasis Lib.
We also conducted the usability test, where we tested the Oasis App.
Apart from that we also added more content to the rapport.

\subsubsection{Sprint Reflection}
In this sprint we learned that not every choice you make as a developer is easy to understand for someone without much technical knowledge.

\subsection{Sprint Eight}
Sprint eight started on 28/05-2012 with a workperiod of eight half days. In this sprint we finished the report.

\subsubsection{Sprint Reflection}
In this sprint we learned that writing some parts of the report earlier might be a good idea.