\section{Unimplemented features}
\label{backlog_unimplemented}

\subsection{Child mode}
\label{backlog:child_mode}
There should be implemented another mode of the launcher which is called child mode. This mode is only for children and is minded on them using it alone without a gardian. In this mode all settings and such is removed and everytime an app is clicked it launches directly with the childs preferences instead of showing the select profile screen.

\subsection{Custom Icons}
\label{backlog:custom_icons}
This feature can change the icon of an app in the app grid. The reason it is important as a feature is seen in \autoref{Preanalysis:Usability_for_children}. 
Recognition is important for children and if they associates an app with another thing e.g. PARROT with a picture well known from their everyday it should be possible for them or their guardian to choose.

\subsection{Hide apps}
\label{backlog:hide_apps}
This feature was meant to be an integration in the drawer \autoref{GUI:drawer} where it should be placed just under the colorpicker. The functionality of this app board is that when an app is unused or should not be acessable for either a child or a guardian it could be put into the drawer and if there was an app in the drawer which the user needed it could be dragged back to the app grid.

\subsection{Home screen modes}
\label{backlog:home_screen_modes}
The home screen should work in both portrait and landscape mode.

\subsection{Lock screen}
\label{backlog:lock_screen}
The lock screen was a feature that WOMBAT needed for when a timer was up and the tablet could not be used any more. The lock screen should be a screen that tells the user that the tablet is now locked and needs to be unlocked.

\subsection{Logo screen loading}
\label{backlog:logo_screen_loading}
There needs to be implemented a way of showing if the logo screen have crashed. The reason is that the logo screen only should run in two seconds and if it takes longer the launcher is probably crashed. 
A possible solution is to implement an loading bar or other form for loading animation.

