\section{Development Method}
In the following section we will discuss the development method, as described in Section \vref{sec:dev_meth}.

\subsection{Agile Development}
Using the agile development method, has given us the ability to adjust according to the requirements coming from the other groups.
The Oasis Lib has been subject for many requirements, coming during sprints, and the agile development method has made it easy to adjust to requirements as they came.

\subsection{Meetings}
In the initial planning phase of the project we held several meetings to discuss which product should be made.
During the project we have been meeting in the multi project group for the start of each sprint, as well as an evaluation at the end of each sprint.
These meetings have given us the ability to follow what the other groups are doing at all times, and therefore plan a bit ahead of the requirements that might come.

\subsection{Sprint Length}
On the meetings at the start of each sprint, we decided how long the sprint should run.
Most sprints ended up being around seven half days of work.
This sprint length was fitting for our group because we could finish some tasks, while keeping up with what the other groups needed.

\subsection{Project Owner}
In this project we had no project owner, this made it a bit harder to decide things in the multi project meetings, as every person had to agree.
However it added the option to influence the project, as an individual, instead of one person deciding it all.
In some situations a project owner would have been able to make a decision and we could have avoided a lot of pointless discussion.