\section{Implemented features}
\label{backlog_implemented}

\subsection{Guardian Mode}
\label{backlog:guardian_mode}
This feature allows guardian users to utilize the \giraf[] system. 
This is currently the only mode in the system.

%\input{chapters/backlog/implemented/profileselect}
\subsection{Profile Select}
\label{backlog:profile_select}
Upon launching an app from the app grid, child profiles are listed, such that the user is allowed to select one of them, prior to app execution.

%\input{chapters/backlog/implemented/authentication}
\subsection{Authentication}
\label{backlog:authentication}
\emph{Authentication} restricts access to data, and allows the launcher to know the identity of the current user.
QR-codes are used to store the credentials of the users, and allows for authentication via the tablets camera, scanning a provided QR-code.

\subsection{Autologin}
\label{backlog:autologin}
\emph{Autologin} enables guardians to start the launcher without authentication, if authentication was performed within the last eight hours.

%\input{chapters/backlog/implemented/GUIcomponents}
\subsection{\guicomponents[]}
\label{backlog:GUI_components}
GUI components are shared using a public library, such that \girafapp[]s can use the same dialogs, buttons, tooltips, widgets, etc.

\subsection{App Grid}
\label{backlog:appgrid}
\emph{App grid} displays icons and titles of \girafapp[]s, and allows the user to launch these.

%\input{chapters/backlog/implemented/homescreen}
\subsection{Homebar and Drawer}
\label{backlog:homebar_drawer}
Information is accessible through a bar -- called ``homebar'' -- as text, images and widgets.
Additional information and functionality is hidden within the homebar, in a drawer, simply called ``drawer''. 
The homebar and the drawer is shown together with the app grid, described in \autoref{backlog:appgrid}.

%\input{chapters/backlog/implemented/logoscreen}
\subsection{Logo Screen}
\label{backlog:logo_screen}
While the launcher is initially loading, a splash screen containing the \giraf[] logo is shown, showing the user that the system is loading.