\section{Reflection}
In our own test phase have been performing these tests in a manner most akin to dynamic black box testing.
We have admittedly operated in a test to pass manner, but we have tested avenues of actions that we suspected could crash the system and did indeed do so.
Also worth noting about our test phase is that while we are developers of the code, it is still black box testing as the test cases were written before the code was.\\
Based on our Test Design's Fail/Succeed Criteria our app has Failed its first testing phase.
We experienced a Critical Error in the `DragDrop' test as the system crashed, and a severe error in the `Perform' test due to the poor handling of a slow application startup.
Of course these things can easily be fixed, but should not be considered acceptable in a finished product, due to our target group.\\

Our Usability Test was based on Dynamic White Box testing, as the questions were based on our knowledge of the code and the Application.\\
Results from the usability tests were somewhat as expected, our design sadly isn't obvious.
However, we never did intend for any user to go without some form of instruction.
We do believe that it is an easy system to learn and remember, even if one might not be able to simply guess how it works.\\

\begin{description}
	\item[Cosmetic 1.] This was a Design Choice, We felt that leaving open spaces between pictograms would be better, expecting that a user would take pictograms in order, or simply rearrange after filling it.
	\item[Cosmetic 3.] This was an oversight on our part, we simply failed to consider that the need for confirmation. A mistake easily fixed by implementing informative Toasts (An Android widget.)
	\item[Severe 1.] In the finished GIRAF system the return button was not supposed to be visible, so we did not handle it being pressed in PARROT.
	\item[Critical 1.] The ``play all'' button was removed after a consultation with our Contact (See Apendix \ref{appendice:notater_fra_tove}), a design choice that might need to reconsidered. This could be remedied by bringing back ``play all'' to the design, or adding smaller play buttons under each pictogram in the sentence board.  
\end{description}


