\section{Remarks and future work}
\label{epi:remarks}
This section is made for the group that comes after us and gets to develop on the launcher. Here it will be possible to find information on what future work we would have done but also which information and experiences we made working in an multi-project group and using agile development.

\subsection{Iterative process}
\label{epi:iterative_process}
When working in an iterative process it is important too meet often in the start of the project periode and later on in the project periode it is important not too have too many meetings. The reason for this is that in the early stages it is really important that all groups have the same vision and know what all the others are doing so dependencies etc. can be figured out and backlogs can be made! Later on it is important that the groups have time to work with their own project, but they should have open door policy, so they get the job done and do not waste their time with meetings which does benefit anything.
We found out that in the startup and onto the rapport writing it was great with sprint with a length of a week or two where often there would be sprint meetings every monday and friday.
We also figured that having people incharge was very important because then the job gets done and everyone knows who will take care of a subject and how to talk to if they have problems with this subject. This could be SVN, commen rapport, test manager, specification manager, design manager etc.

\subsection{Development}
\label{epi:development}
The forward development of the launcher is very important because it provides functionality both to the users of the \giraf[] system but also all other apps in \giraf[].
The first steop is to fix all bugs found in \autoref{test:known_bugs} and in the usability test results \autoref{table:usability_results} in test \autoref{sec:usability_test}. Maybe even run an early test giving the guardian the tables in Egebakken to try for a week and see if this will reveal even more bugs or bad design decisions.

\subsubsection{Modes}
\label{epi:modes}
The two modes represented in the \giraf[] system is the guardian- and child mode. As seen in \autoref{chap:backlog} only the guardian mode was implemented. Therefore it is possible that the next step the launcher should take is to include child mode so children can use the tablet alone without a guardian.

\subsubsection{\giraf[] GUI components}
\label{epi:giraf_GUI_components}
The \giraf GUI library was implemented and works great, maybe it needs to be enforce to some of the other apps in the system, and should definatly still be used to place all GUI elements which every group can benefit from.
One step to take in the future is to include even more elements in this library so, in the end, it will include all kinds of graphics from buttons to color pickers and replace the Android standart ones.