This report was written as a 6th semester bachelor project by Software group sw604f12 from the Department of Computer Science at Aalborg University (AAU) in the spring of 2012. The report will document the process of developing an administration module for the GIRAF system. The GIRAF system is designed to support guardians of children with autism spectrum disorder.

When references are used in the report they will be referred to in the format [abc] with a corresponding entry in the bibliography (located in the back of the report). For larger works a range of relevant pages will also be specified in the format [p.~10-11]. Figures, tables and equations will be referred to in the format [2.1], where the first number refers to the chapter in which it is placed and the second number is the actual number of the figure, table or equation.

The reader is expected to have an understanding of basic programming concepts.

Throughout this report the following abbreviations will be used:

\begin{itemize}
	\item GIRAF - Name of the entire system, a title was never agreed upon, but ``\textbf{G}raphical
	\textbf{I}nterface \textbf{R}esources for \textbf{A}ssistive \textbf{F}unctionality'' was suggested.
	\item WOMBAT - Name of the timer application, \textbf{W}ay \textbf{O}f \textbf{M}easuring \textbf{Ba}sic \textbf{T}ime. 
	\item PARROT - Name of the pictogram application, \textbf{P}ictogram \textbf{A}ssisting with \textbf{R}hetoric \textbf{R}easoning \textbf{O}r \textbf{T}alking.
	\item MVC - \textbf{M}odel \textbf{V}iew \textbf{C}ontroller \cite{MVC}.
	\item ASD - Autistic Spectrum Disorder.
	\item Guardians - Parents, teachers, caretakers, and educators of children with ASD.
	\item Children - Children refers to ``Children with ASD''.
	\item We - In the introduction, it refers to the entire multi project group. After the common report, it refers to the individual project group.
	\item Eclipse - An intelligent development environment for Java.
	\item Metadata - Data about data.
	\item API - \textbf{A}pplication \textbf{P}rogramming \texbf{I}nterface.
\end{itemize}

\\ \\

The CD-ROM included with this report contains the source code for the system developed during this project, as well as a copy of this report.

The Oasis administration project group would like to thank the educators whom helped developing and designing the GIRAF system, as well as our supervisor for the interest and cooperation in the project.