\chapter*{Preface}
\label{preface}

We would like to thank our supervisor Ricardo Gomes Lage and Ren\'e Rydhof Hansen for helping and supervising throughout the project.
Furthermore we would like to thank the people of HiTechnic for the support with their hardware.

The following report details the process of creating a \roadtrain{} with \lego{} cars using the \lego{} NXT.

In the report the following notations will be used:

The leader car will be referred to as the \runner{}, and the follower car will be referred to as the \stalker{}.

\paragraph{Quotations} are the words of another person along with a source.
The source of the citation will either be in the text immediately before or after, or could potentially be incorporated into the quote as shown in the example below: \\

\myQuoteA{This is an example of a quotation.}{X, p.~Y}

\paragraph{References} are references to sections, figures, code snippets, chapters or parts written elsewhere in the report. 
This could look like the following:\\

This is explained in Section~X.Y.

\paragraph{Code examples} are written in a special environment so they are easy to read and recognize. 
Examples can be seen in Code~snippet~\ref{chelloworld}. 
Whenever there is a sequence of three dots (``...'') in a code snippet, it means that we have omitted some content, which is not important in that specific context.

\begin{lstlisting}[style=sourceC, caption={Code example of a hello world program written in C.}, label=chelloworld]
#include<stdio.h>

main()
{
    printf("Hello World");
}
\end{lstlisting}