One of the goals of this semester is to show that we have knowledge in choosing and implementing different work methods and apply the method that we find most suited for our project. In order to do this one must first know the different methods before he/she will be able to choose the best suited. 

Different work methods can be put into two categories: Traditional and Agile.
The difference of traditional and agile methods are what they emphasizes the most.

Traditional methods puts big emphasize on analyzing the problem and create documentation of the analysis. The structure of a traditional method is therefore often split into phases, for instance the analysis phase or the implementation phase. Once a phase is done you move to the next phase. An example of this is the waterfall method. [put some example]

Agile methods on the other hand puts emphasis on analysis and documentation in a different way. Most agile methods utilizes an iteration driven work style. This means that you do all the phases over and over. This also means that you do not do the whole project at once. Instead you focus on getting a part of the system to work and then as more iterations are completed you add on to the system until the system is ready to be released. An example of this is the SCRUM method. [put some example]

Both approaches have strength and weaknesses. The traditional method features lots of documentation and analysis and so it is easier for others to understand if they are to develop further on the system. It also create a great overview of the whole system, and thus it is easier to estimate how long time it will take before the system is ready to ship. This makes traditional methods well suited for large projects. The agile method on the other hand implements the iteration driven approach. One of the great features of this approach is that you can correct errors and include things you might have forgotten relatively easy, because you just do it in the next iteration. 

One of the big drawbacks of the traditional method is that you cannot just go back a step, if you realize you have forgotten something or made an error. This is very costly because you have to do lots of steps over again. Another big issue with the traditional method is that the customers of the system might not always know what they want or need at the start of the development, but this is where you do all the analysis. The Agile method excels at this as you can present to your customers your current build and receive feedback that you might not have considered. 

The Work method that we find best suited for our project is an agile method. This is because in this semester we are working together with educators from institutions working with children with ASD. They will have requirements for our system so it is important that we are taking them into the project. It is also important that we choose a development method that have tools for managing bigger project groups as we are working as part of a bigger team to develop a system.

We have considered These following agile work methods:

\begin{itemize}
\item Scrum
\item Xp 
\end{itemize} 

In short Scrum is a method that emphasizes a self-directed and self-organizing team, each iteration is client driven meaning that the clients provides the requirements and features will be prioritized according to the clients needs.

XP emphasizes programming and testing. This means that there are very little documentation of the system other than the code. A simple design is preferred and the code is refactored with high frequency. This method requires high discipline since most planning is done orally.

