%futureWork.tex
As previously stated, the system is very open for future work. In this section our suggestion on what to do is listed.

\subsection*{Serverside}
Of the issues discussed in \autoref{sect:disc}, 
the most important thing to implement, is the communication between Savannah and Oasis. To do this, it is required to import the ServerConnection.jar into Oasis. This should, in theory, be enough to enable the communication. Furthermore, the communication protocol, must be changed form TCP/IP to SSL, when the system goes live, as this is a major security issue at the moment.
As a product Savannahs server is still in a primitive state, and many hours of continued development could be put into it.


\subsection*{Web Interface}
The web interface is the part that has be most future work to be done:
\begin{description}
	\item[Main screen] The major focus should be on implementing a working main screen after login.
	\item[Security] Only authenticated uses should be able to access specific data.
	\item[Usability] The results of the usability test should be incorporated, to ease the use of the web interface
	\item[Eye candy] Color schemes, button layout etc. should be changed to fir the general ``atmosphere'' of the GIRAF system.
\end{description}
Implementing the main screen after login, will make it quite easy to increase the security, this will also enable the implementation of retrieval and editing of settings, and generation of stats. Furthermore most of the functionality needed beyond login (edit user, add pictures to the user, assign children/guardians, etc.) are already present, they merely needs to be relocated.