%TODO mangler intro
The following section concerns requirements gathering done in the multi project group, as well as the continuous requirements gathering done in the project group.

\subsubsection*{Initial Requirements Gathering}
Requirements gathering was done in the multi project group in the early stages of the project, with continuous requirments gathering throughout the project.
In the initial stages we did semi-structured interviews with our customers, where the primary focus was understanding our target group and exploring any tools they currently have access to, while allowing the customers to present their own ideas and visions of the project.

From these interviews we created an initial list of requirements for the multi project.

Three interviews were done: Mette and Kristine from Birken\footnote{A kindergarten for children with special needs}, Drazenko from Egebakken\footnote{A school for children with special needs}, and Tove from Taleinstituttet\footnote{The speech center}.
From the interviews we gathered a list of their ideas and visions, and made a requirements list that the project groups can consult.

\begin{itemize}
 \item Mette And Kristine 
  \subitem Customizable software
  \subitem Ease of use, compared to current physical tools
  \subitem Emphasize visual stimuli
  \subitem Continuous stimuli 
 \item Drazenko
  \subitem Customizable software
  \subitem Visual abstract concept
  \subitem Emphasize visual stimuli
  \subitem Unambiguous
  \subitem Consistency/structure
 \item Tove 
  \subitem Customizable software
  \subitem Engaging/entertaining software
  \subitem Authentic/proper feedback or behavior
\end{itemize}

A list of common requirements have been created:

\begin{itemize}
 \item Customizable software
  \subitem Some way to distinguish unique users on the same tablet is required, since people with ASD have different needs and have very different perceptions of the world.
  \subitem Customization is more important than many features.
 \item Emphasize visual stimuli
  \subitem People with ASD are visually over-stimulated.
 \item Authentic/proper feedback or behavior
  \subitem If a dog is depicted in an application, it should act, sound, and feel like a dog.
\end{itemize}


\subsubsection*{Continuous Requirements Gathering}
As an integral part of Scrum, we have had continuous requirements gathering.
For Savannah, the continuous requirements gathering comes from discussing the needs of Savannah with the other project groups, as well as talks with the customers
during the project.

During the project we have gathered these requirements:
\begin{itemize}
 \item PARROT
  \subitem Linking audio and images in the database.
 \item Launcher
  \subitem QR-code support and storage in the database.
  \subitem A live test of the connection to Savannah (ping functionality).
 \item Oasis
  \subitem Retrieval styles: Full profile or children associated with a specific guardian.
 \item Customers
  \subitem Changes to the web interface.
 \item Multi project group
  \subitem Secure connection
\end{itemize}

The majority of requirements for Savannah has come through cooperation with the Oasis group during the design phase of the database, which was a running process that ended
at the beginning of the $4^{th}$ sprint, where the database was frozen. Any requirements that may have arrived beyond this point was added to the project backlog for future development.
The requirement listed as being set by the multi project group regarding a secure connection, was a descission made in the multi project group. The reasoning is that the system could be 
handling potentially sensitive personal data, and as such secure communication is a requirement when the server is ready for deployment.